Cross-Validation Default

### 2023-11-17 minos/validation/cross_validation_default.Rmd
slight bug fix

format_child_age_data <- function(dataset) {
  formatted.age.data <- dataset %>%
                        dplyr::select(hidp, time, child_ages, pidp) %>%
                        filter(time >= 2014) %>%
                        group_by(pidp, time) %>%
                        summarise(child_ages = max(child_ages))

@@

format_nkids_data <- function(dataset) {
  dataset %>%
  group_by(time, hidp) %>%
  summarise(nkids = max(nkids)) %>%
  #group_by(time) %>%
  #summarise(nkids_by_year = sum(nkids_counts))
  return (dataset)
}

>>>>

format_child_age_data <- function(dataset) {
  formatted.age.data <- dataset %>%
                        dplyr::select(hidp, time, child_ages, pidp) %>%
                        filter(time >= 2014) %>%
                        group_by(time, pidp) %>%
                        summarise(child_ages = max(child_ages))

@@

format_nkids_data <- function(dataset) {
  dataset %>%
  group_by(hidp, time, pidp) %>%
  summarise(nkids = max(nkids)) %>%
  #group_by(time) %>%
  #summarise(nkids_by_year = sum(nkids_counts))
  return (dataset)
}
